---
title: "Gun Control Chi Square"
author: "Bridget Gibbons"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Bridget and I'm updating this markdown file here.

```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")
```

We are asking: Is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get)?

Hi Bridget: This is Robert testing to see if our collaboration is working. 

Bridget: data wrangling and counts

```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
  
```

My name is Robert the Collaborator and I'm going to be doing Chi-square test for independence!

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}

# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# The "1"" at the end of the call in prop.table gives the proportion within each row


# Run a chi-square test for independence

guns_x2 <- chisq.test(get_guns)
guns_x2


```

# Recommended government action on gun access differed significantly between male (n= ) and female (n= ) respondents ($\chi^2$(`r guns_x2$parameter`)..., = p<0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compared to male respondents (40.4%). 
